Predicting Kamala Harris's Victory in the 2024 US Election

### 2024-10-24 paper/paper.qmd
Update Abstract

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Xuanle Zhou
  - Yongqi Liu
  - Yuxuan Wei
thanks: "Code and data are available at: https://github.com/wyx827/2024USpresidentialelection.git."
date: today
date-format: long
toc: true
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Predicting Kamala Harris's Victory in the 2024 US Election"
subtitle: "An Investigation into Poll Data Using Multiple Linear Regression"
author: 
  - Xuanle Zhou
  - Yongqi Liu
  - Yuxuan Wei
thanks: "Code and data are available at: https://github.com/wyx827/2024USpresidentialelection.git."
date: today
date-format: long
toc: true
abstract: "This study predicts the outcome of the 2024 U.S. presidential election using multiple regression analysis based on state-by-state electoral votes. The predictive model offers prediction that can inform campaign strategies and shape public discourse. Results suggest a strong likelihood of Kamala Harris securing victory in the 2024 election cycle."
format: pdf
number-sections: true
bibliography: references.bib
---
